---
title: "ECON 121 FA24 Final Exam"
author: "Your name"
output: pdf_document ## or html_document
---

```{r setup, include=FALSE}
# set the code chunk format
knitr::opts_chunk$set(echo = TRUE)
# clear the environment
rm(list=ls())
# load all packages from the course
library(tidyverse)
library(fixest)
library(marginaleffects)
# you do not need any other packages for the exam.
# if you load other packages, we cannot help you 
# troubleshoot any resulting knitting problems.
```

## In-person codeword (disregard if taking the exam remotely)



## Question 1

```{r}
# Your code here
```

\newpage

## Question 2

Your verbal answer here

\newpage

## Question 3

```{r}
# Your code here
```

\newpage

## Question 4

Your verbal answer here

\newpage

## Question 5

```{r}
# Your code here
```

\newpage

## Question 6

Your verbal answer here

\newpage

## Question 7

```{r}
# Your code here
```

\newpage

## Question 8

Your verbal answer here

\newpage

## Question 9

```{r}
# Your code here
```
\newpage

## Question 10

Your verbal answer here

\newpage

## Question 11

```{r}
# Your code here
```

\newpage

## Question 12

Your verbal answer here

\newpage

## Question 13

```{r}
# Your code here
```

\newpage

## Question 14

Your verbal answer here

\newpage

## Question 15

```{r}
# Your code here
```

\newpage

## Question 16

Your verbal answer here

\newpage

## Question 17

```{r}
# Your code here
```

\newpage

## Question 18

Your verbal answer here

\newpage

## Question 19

```{r}
# Your code here
```

\newpage

## Question 20

Your verbal answer here







